Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-03-07 co-regular-PQ.tex
I prove the co-regular of five rules

We say that $\textit{PQueue}$ is regular, if each of its rule is co-regular.
\end{definition}

@@

>>>>

We say that $\textit{PQueue}$ is co-regular, if each of its rule is co-regular.
\end{definition}

@@

\subsection{Combine Step-by-Step linearizability and Co-Regular}
\label{subsec:combine step-by-step linearizability and co-regular}

We also prove that $\textit{PQ}_2^{>}$, $\textit{PQ}_2^{=}$ and $\textit{PQ}_3$ are co-regular. The case of $\textit{PQ}_2^{>}$ is quite simple, since whenever $\textit{last}(e) = \textit{PQ}_2^{>}$, $e \sqsubseteq \textit{MS}(\textit{PQ}_2^{>})$. For the case of $\textit{PQ}_2^{=}$, we find a necessary and sufficient condition for violating $\textit{MS}(\textit{PQ}_2^{>})$, and shows that such condition violates the assumptions that every single-priority execution is FIFO and can be safely ignored. For the case of $\textit{PQ}_3$, it can be similarly proved as the rule for $\textit{deq}(\textit{empty})$ in \cite{Bouajjani:2015}. We leave the detailed proof of co-regular of these three rules in Appendix \ref{subsec:appendix co-regular of PQ2Lar}, Appendix \ref{subsec:appendix co-regular of PQ2Equal} and Appendix \ref{subsec:co-regular of PQ3}, respectively.

Now we can see that $\textit{PQueue}$ is co-regular, which is a direct consequence of co-regular of each of its rules, and is stated below.

\begin{restatable}{lemma}{PQueueIsCoRegular}
\label{lemma:PQueue is co-regular}
$\textit{PQueue}$ is co-regular.
\end{restatable}

Since we have already prove that $\textit{PQueue}$ is step-by-step linearizability and co-regular, we can now reduce the verification of linearizability with respect to $\textit{PQueue}$ into a reachability problem, as illustrated by the following theorem. Here $\textit{Auts}$ is the set of witness automata of this section.

\begin{restatable}{theorem}{ReducePQueueIntoStateReachability}
\label{lemma:reduce PQueue into state reachability}
Given a data-independence implementation $\mathcal{I}$. $\mathcal{I} \sqsubseteq \textit{PQueue}$, if and only if, $\mathcal{I} \cap \textit{Auts} = \emptyset$.
\end{restatable}
